%------------------------------------
% Dario Taraborelli
% Typesetting your academic CV in LaTeX
%
% URL: http://nitens.org/taraborelli/cvtex
% DISCLAIMER: This template is provided for free and without any guarantee
% that it will correctly compile on your system if you have a non-standard
% configuration.
% Some rights reserved: http://creativecommons.org/licenses/by-sa/3.0/
%------------------------------------

%%% Local Variables:
%%% mode: latex
%%% TeX-engine: xetex
%%% TeX-PDF-mode: t
%%% TeX-master: t
%%% End:

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[10pt, a4paper]{article}
\usepackage{fontspec}

% DOCUMENT LAYOUT
\usepackage{multicol}
\usepackage{geometry}
\geometry{letterpaper, textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in}
\setlength\parindent{0in}

% FONT
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text}
\setromanfont [Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Linux Libertine}
\setmonofont[Scale=0.8]{Monaco}

% ---- CUSTOM COMMANDS
\chardef\&="E050
\newcommand{\html}[1]{\href{#1}{\scriptsize\textsc{[html]}}}
\newcommand{\pdf}[1]{\href{#1}{\scriptsize\textsc{[pdf]}}}
\newcommand{\doi}[1]{\href{#1}{\scriptsize\textsc{[doi]}}}
% ---- MARGIN YEARS
\usepackage{marginnote}
\newcommand{\amper{}}{\chardef\amper="E0BD }
\newcommand{\years}[1]{\marginnote{\scriptsize #1}}
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt}
\reversemarginpar

% HEADINGS
\usepackage{sectsty}
\usepackage[normalem]{ulem}
\sectionfont{\mdseries\upshape\Large}
\subsectionfont{\mdseries\scshape\normalsize}
\subsubsectionfont{\mdseries\upshape\large}

% PDF SETUP
\usepackage[bookmarks=true, colorlinks=true, breaklinks=true,
	pdftitle={Cameron Higby-Naquin resume},
	pdfauthor={Cameron Higby-Naquin},
	pdfproducer={http://nitens.org/taraborelli/cvtex}
]{hyperref}
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue}

% DOCUMENT
\begin{document}
{\LARGE Cameron Higby-Naquin}\\
\begin{multicols}{2}
248 North Avenue\\
Burlington, VT 05401
\vfill
\columnbreak
\begin{tabular}{ll}
\textsc{phone}:&(505) 307-9277\\ % ()
\textsc{email}:&\href{mailto:me@chigby.org}{me@chigby.org}\\
\textsc{url}:&\href{http://chigby.org/}{http://chigby.org}\\
\end{tabular}
\end{multicols}

%%\hrule
\section*{Professional Experience}
\noindent
\years{2009-2012}\textbf{AWeber Communications, Inc.}\\
\textit{A web-based email marketing solution used by over 115,000 customers.}\\
Web Developer
\begin{itemize}
\item Created a simple, data-rich interface for customers to act on statistics about their emails.
\item Redesigned the message archive, a browsable web interface viewed by millions of subscribers.
\item Developed a tool for businesses to easily connect PayPal purchases with email lists. % could also mention Zendesk widget, Wordpress plugin here.
\item Led the upgrade of an aging support ticket system to cloud-based solution Zendesk.
\item Created a system to automate frequent support phone calls, saving employees from having to make hundreds of calls per day.
% gift code generator (automated postal mail?), bar code scanner?
\end{itemize}
% Resposible for the development and maintenance of an email marketing solution used by over 115,000 customers.  Worked in small teams to create new features for users and internal tools to maintain and support the application.  Heavily involved in projects to improve customer understanding and usage of email statistics, enhanced web-based displaying of messages, and integration with other services (PayPal, Wordpress, ZenDesk).  Also lead the upgrade of the aging support ticket manager to a fully modern, web-based solution, and created a system to automate certain common phone interactions, freeing up employees' time. \\

\years{2006-2009}\textbf{OPG Global, Inc.}\\
\textit{A company specializing in web products and reports for HR professionals.}\\
Manager, Sites, Systems \& Technologies {\scriptsize (2007-2009)}\\
Web Developer {\scriptsize (2006-2007)}
\begin{itemize}
\item Managed and supervised a small team of web designers and developers.
\item Created a unified content management system to streamline updates to multiple websites.
\item Created an automated calendar to schedule email newsletters and marketing distributions.
\item Spearheaded the implementation of version control and .NET over classic ASP.
\item Worked with project managers to design and deploy finished production sites.
\end{itemize}
% Managed a small team of web designers and developers to create a variety of web products for HR professionals.  Spearheaded the implementation of new processes and technologies, including a unified content management system for multiple websites, an automated calendar system to schedule email newsletters and marketing distributions, and version control for developers to collaborate more easily.  Worked extensively with project managers to design and deploy finished production websites.\\

\section*{IT \& programming skills}
\noindent
Databases (PostgreSQL, MongoDB, MySQL, Redis, Memcached)\\
Frameworks (Flask, Pylons, CakePHP, ASP.NET)\\ % Rails?
Operating Systems (Mac OS X, Linux, Windows)\\
Programming Languages (Python, PHP, Perl, Javascript, Shell script, Ruby)\\ % C#, IDL
Markup Languages (HTML5, CSS)\\ % not sure if I want \texttt{}
Revision Control (Git, Subversion)\\
Digital Typesetting (\LaTeX, \XeTeX)\\
Server Provisioning (Puppet)\\

%\hrule
\section*{Education}
\noindent
\years{2005}\textbf{Bachelor of Arts in Astrophysics} {\scriptsize (awarded high honors)}\\
\textit{Swarthmore College}, Swarthmore, PA

%\hrule
\section*{Dance leadership experience} % "dance organization"?
\noindent
\years{2006-present}\textbf{Germantown Country Dancers}\\
Webmaster {\scriptsize (2012-present)}\\
Treasurer {\scriptsize (2008-2012)}\\
Board of Directors At-Large Member {\scriptsize (2006-2008)}\\

%\vspace{1cm}
\vfill{}
%\hrulefill

\begin{center}
{\scriptsize  Last updated: \today\- •\-
% ---- PLEASE LEAVE THIS BACKLINK FOR ATTRIBUTION AS PER CC-LICENSE
Typeset in \href{http://nitens.org/taraborelli/cvtex}{
\fontspec{Times New Roman}\XeTeX }\\
% ---- FILL IN THE FULL URL TO YOUR CV HERE
\href{http://chigby.org/resume.pdf}{http://chigby.org/resume.pdf}}
\end{center}

\end{document}